\documentclass[../main.tex]{subfiles}

\setcounter{section}{3}

\begin{document}

\setcounter{exercise}{6}
\begin{exercise}
  Suppose vector space $V$ and $W$ are finite $(2 \le \dim V \le \dim W)$,
  show that $\set{T \in \LT(V, W)}{T \text{ is not injective}}$ is not a subspace.
\end{exercise}
\begin{proof}
  Consider the basis $\join[+]{v}{(\dim V - 1)} \in V$,
  and $T(\join[+]{v}{(\dim V - 1)}) = (0 + \join[+]{1}{(\dim V - 1)})$
  and $T^\prime(\join[+]{v}{(\dim V - 1)}) = (v_0 +  0 + \cdots + v_{(\dim V - 1)})$.
  Then
  $(T + T^\prime)(\lambda_0v_0 + \lambda_1v_1 + \cdots + \lambda_{(\dim V - 1)}v_{(\dim V - 1)}) = \lambda_0v_0 + \lambda_1v_1 + \cdots + 2\lambda_{(\dim V - 1)}v_{(\dim V - 1)}$,
  which is obviously injective.
\end{proof}

\setcounter{exercise}{10}
\begin{exercise}
  Suppose $V$ is finite and $T \in \LT(V, W)$, show that there is a subspace $U \subset V$ such that:
  \[
  U \cap \nullv T = \0 \quad \text{and} \quad \rangev T = \set{Tu}{u \in U}
  \]
\end{exercise}
\begin{proof}
  This is similar to the \textit{isomorphism theorems} about groups!
  This can be done by the similar way we used in proving $\dim V = \dim \nullv T + \dim \rangev T$.
\end{proof}

The next two exercises remind me the categorical injective and surjective, let try them first!

\begin{exercise*}
  For any $F \in \LT(V, W)$, $F$ is injective $\iff$ for any $S, T \in \LT(U, V)$, $FS = FT$ implies $S = T$.
\end{exercise*}
\begin{proof}
  ~
  \begin{itemize}
    \item $(\Rightarrow)$ For any $S, T \in \LT(V, W)$ that $FS = FT$, then for any $u \in U$,
          we have $F(Su) = F(Tu)$, since $F$ is injective, we know $Su = Tu$, so $S = T$.
    \item $(\Leftarrow)$ For any $v, w \in V$ such that $Fv = Fw$. Consider
          \begin{align*}
            S(\lambda) &= \lambda v \\
            T(\lambda) &= \lambda w
          \end{align*}
          in $\LT(\mathbb{R}, V)$.
          Then for any $\lambda \in \mathbb{R}$, we have $FS\lambda = \lambda FS1 = \lambda Fv = \lambda Fw = \lambda FT1 = FT\lambda$.
          so $FS = FT$ then $S = T$, which means $v = S1 = T1 = w$.
  \end{itemize}
\end{proof}

\begin{exercise*}
  Suppose $W$ is finite, then for any $F \in \LT(V, W)$, $F$ is surjective $\iff$ for any $S, T \in \LT(W, U)$, $SF = TF$ implies $S = T$.
\end{exercise*}
\begin{proof}
  ~
  \begin{itemize}
    \item $(\Rightarrow)$ For any $S, T \in \LT(W, U)$ such that $SF = TF$. For any $w \in W$,
          there is $v \in V$ such that $Fv = w$ since $F$ is surjective. Then we have
          $SFv = TFv$ so $Sw = S(Fv) = T(Fv) = Tw$ then $S = T$.
    \item $(\Leftarrow)$ Consider
          \[
          S = I \quad \text{and} \quad T(\lambda_0w_0 + \cdots + \lambda_n w_n) = \lambda_0w_0 + \cdots + \lambda_kw_k
          \]
          where $\join{w}{k}$ is the basis of $\rangev F$ and
          $\join{w}{n}$ is the basis of $W$ that expand from $\join{w}{k}$.

          It is easy to show that $T$ is a linear transformation. Then for any $v \in V$, we have
          $TFv = Fv$ (since $T$ acts like identity transformation on $\rangev F$) and $SFv = Fv$,
          so $S = T$ by the property of $F$. Since $\rangev S = W$, so is $\rangev T$, that means
          $\join{w}{k}$ spans $W$, so $k = n$, which means $\rangev F = W$, therefore $F$ is surjective.
  \end{itemize}
\end{proof}

\setcounter{exercise}{18}
\begin{exercise}
  Suppose $W$ is finite, then for any $T \in \LT(V, W)$,
  show that $T$ is injective $\iff$ there is $S \in \LT(W, V)$ such that $ST = I$.
\end{exercise}
\begin{proof}
  ~
  \begin{itemize}
    \item $(\Rightarrow)$ Consider the basis $\join{v}{n}$ of $V$, then $Tv_0, \cdots, Tv_n$
          is a basis of $\rangev T$ since $T$ is injective. We denote $Tv_i$ as $w_i$
          and $\join{w}{m}$ as the basis of $W$ which expand from $\join{w}{n}$.
          Define $S(\joinp[+]{\lambda}{w}{m}) = \joinp[+]{\lambda}{w}{n}$, and then for any
          $v \in V$, $ST(\joinp[+]{\lambda}{v}{n}) = S(\lambda_0w_0 + \cdots + \lambda_nw_n) = \joinp[+]{\lambda}{v}{n}$,
          so $ST = I$.
    \item $(\Leftarrow)$ Suppose $A, B \in \LT(U, V)$, such that $TA = TB$, we will show that $A = B$.
          $STA = IA = A$ and $STB = IB = B$ and $STA = STB$ since $TA = TB$.
          Then we know $T$ is a monomorphism, and then $T$ is injective.
  \end{itemize}
\end{proof}

\begin{exercise}
  Suppose $W$ is finite, then for any $T \in \LT(V, W)$,
  show that $T$ is surjective $\iff$ there is $S \in \LT(W, V)$ such that $TS = I$.
\end{exercise}
\begin{proof}
   
\end{proof}

\end{document}